Assignment 8
---

"When life gives you lemons, don’t make lemonade. Make life take the lemons back! Get mad!" -Cave Johnson

For this assignment, you'll be using the lemons dataset, which is a subset of the dataset used for a Kaggle competition described here: 
https://www.kaggle.com/c/DontGetKicked/data. Your job is to predict which cars are most likely to be lemons. 

Complete the following steps.
```{r libraries}
library(tidyverse)
library(knitr)
library(caret)
library(forcats)
library(tidytext)
library(stringr)
library(AUC)
```
1. Calculate the proportion of lemons in the training dataset using the `IsBadBuy` variable. 
```{r}
lemon%>%
count(IsBadBuy)%>% 
mutate(p=prop.table(n))%>% 
kable(format="markdown") 
```
2. Calculate the proportion of lemons by Make. 
```{r}
g_table<-table(lemon$Make,lemon$IsBadBuy);g_table

prop.table(g_table,margin=1)
```
3. Now, predict the probability of being a lemon using a linear model (`lm(y~x`), with covariates of your choosing from the training dataset. 
```{r}
lm_mod<-lm(IsBadBuy~
             Make+
             WheelType+Nationality+Transmission+Auction,
           data=lemon,y=TRUE,na.exclude=TRUE);summary(lm_mod)
```
4. Make predictions from the linear model.
```{r}

lm_predict<-predict(lm_mod)


lm_predict_bin<-ifelse(lm_predict>.5,1,0)


lm_table<-table(lm_predict_bin,lm_mod$y)

pcp<-(lm_table[1,1]+lm_table[2,2])/sum(lm_table)

pred_table<-prop.table(lm_table,margin=1)

View(pred_table)
```
5. Calculate the AUC for the linear predictions from the ROC against the outcome for the training dataset. 
```{r}
lm_predict_no_na<-na.omit(lm_predict)

lm_roc<-roc(lm_predict_no_na,as.factor(lm_mod$y))

auc(lm_roc)
 
plot(lm_roc)
```
6. Now, predict the probability of being a lemon using a logistic regression
(`glm(y~x,family=binomial(link="logit")`)), again using covariates of your choosing. Add these to the existing linear model already give to you.  
```{r}
logit_mod<-glm(IsBadBuy~
             Make+
             WheelType+Nationality+Transmission+Auction,
             data=lemon,
            na.action=na.exclude,
            family=binomial(link="logit"),
               y=TRUE)

summary(logit_mod)

```
7. Make predictions from the logit model. Make sure these are probabilities. 
```{r}
logit_predict<-predict(logit_mod,type="response")
logit_predict_bin<-rep(0,length(logit_predict))

logit_predict_bin[logit_predict>=.5]<-1

logit_table<-table(logit_predict_bin,lemon$IsBadBuy)

pcp_logit<-(logit_table[1,1]+logit_table[2,2])/sum(logit_table)

pred_table<-prop.table(lm_table,margin=1)

View(pred_table)
```
8. Calculate the AUC for the predictions from the ROC based on the logit model. 
```{r}
logit_predict_no_na<-na.omit(logit_predict)

logit_roc<-roc(logit_predict_no_na,as.factor(logit_mod$y))

auc(logit_roc)
 
plot(logit_roc)
```
